Functional Analyses of Distinct Oxygen Concentrations and Light Niches of *Prochlorococcus marinus*

### 2024-01-18 Code/Manuscript_O2.Rmd
Generated new plots

---
title: "Functional Analyses of Distinct Oxygen Concentrations and Light Niches of *Prochlorococcus marinus*"
author:
  - name: '**Mireille Savoie**'
    affil: 1
    main: true
    email: msavoie@mta.ca
  - name: Julie Nadeau
    affil: 1
  - name: Laurel Genge
    affil: 1
  - name: Sylwia Śliwińska-Wilczewska
    affil: 1,2
  - name: Maximilian Berthold
    affil: 1
  - name: Naaman Omar
    affil: 1
  - name: Douglas A. Campbell
    affil: 1
    main: false
    orcid: ''
    email: 'dcampbel@mta.ca'
affiliation:
  - num: 1
    address: Department of Biology, Mount Allison University
institute:
  - mta: 'Department of Biology, Mount Allison University, 53 York St., Sackville NB, Canada, E4L 1C9.'
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::word_document2:
    code_folding: show
    reference_docx: KnitTemplate.docx
    keep_md: yes
    toc: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
always_allow_html: true
bibliography: [Prochlorococcus_O2_NPQ.bib, RPackages.bib]
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

>>>>

---
title: "Functional Analyses of Distinct Oxygen Concentrations and Light Niches of *Prochlorococcus marinus*"
author:
  - name: '**Mireille Savoie**'
    affil: 1
    main: true
    email: msavoie@mta.ca
  - name: Julie Nadeau
    affil: 1
  - name: Laurel Genge
    affil: 1
  - name: Sylwia Śliwińska-Wilczewska
    affil: 1,2
  - name: Maximilian Berthold
    affil: 1
  - name: Naaman Omar
    affil: 1
  - name: Douglas A. Campbell
    affil: 1
    main: false
    orcid: ''
    email: 'dcampbel@mta.ca'
affiliation:
  - num: 1
    address: Department of Biology, Mount Allison University
institute:
  - mta: 'Department of Biology, Mount Allison University, 53 York St., Sackville NB, Canada, E4L 1C9.'
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::word_document2:
    code_folding: show
    reference_docx: KnitTemplate.docx
    keep_md: yes
    toc: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
always_allow_html: true
bibliography: [Manuscript_O2.bib, RPackages.bib]
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

```{r MED4ProteinAttonated, fig.cap = MED4ProteinAttonated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MED4ProteinAttonated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade).  **",

                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
                    "Numbers over each bar are fmole/ug",

knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAttonated.png"))
```

```{r MIT9313ProteinAttonated, fig.cap = MIT9313ProteinAttonated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MIT9313ProteinAttonated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",

                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
                    "Numbers over each bar are fmole/ug",

knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAttonated.png"))
```
